Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/visibility.tex
Working on 2

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tabular}{cc|cc}
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.75,2.75);
                \draw[dashed] (0,0) -- (2,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
                \filldraw[black] (2,1) circle (0.05) node[anchor=north] {q1};
                \draw [thick] (0,0) -- (0.5,0) -- (1,0) -- (1,0.5) -- (1.5,0.5) -- (1.5,1) -- (2,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,0.5) -- (0.5,0.5) -- (0.5,1) -- (1,1) -- (1,1.5) -- (2.5,1.5) -- (2.5,0.5) -- (2,0.5) -- (2,0) -- (1.5,0) -- (1.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture} & & &
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (3.25,3.25);
                \draw[red,dashed,thick] (0,0) -- (1.5,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
                \filldraw[black] (1.5,1) circle (0.05) node[anchor=north] {q2};
                \draw [thick] (0,0) -- (0,1) -- (0.5,1) -- (0.5,1.5) -- (1,1.5) -- (1,1) -- (1.5,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (0,1.5) -- (0,2) -- (1.5,2) -- (1.5,1.5) -- (2,1.5)  -- (2,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture} \\
            Visible                       & & & Non Visible                   \\\\
            \hline\\
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,0);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
                \filldraw[black] (1,0) circle (0.05) node[anchor=north] {q3};
                \draw [thick] (0,0) -- (0,1) -- (1,1) -- (1,0);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,-0.5) -- (-0.5,-0.5) -- (0.5,-0.5) -- (0.5,0.5);
            \end{tikzpicture} & & &
            \begin{tikzpicture}
                \draw[step=0.5,lightgray,thin,xshift=-1cm,yshift=-1cm] (0.25,0.25) grid (2.75,2.75);
                \draw[red,dashed,thick] (0,0) -- (1,1);
                \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
                \filldraw[black] (1,1) circle (0.05) node[anchor=north] {q4};
                \draw [thick] (0,0) -- (0,1) -- (1,1);
                \draw[thick,dashed] (-0.5,-0.5) -- (-0.5,1.5) -- (1.5,1.5) -- (1.5,0.5) -- (0.5,0.5) -- (0.5,-0.5) -- (-0.5,-0.5);
            \end{tikzpicture}\\
            Non Visible (from a 1-d cell) & & & Non Visible (from a 0-d cell)
        \end{tabular}
        \caption{Examples of visibility in 2D.}
        \label{fig:visibility-2d}
    \end{figure}

>>>>

    % Examples of visibility in 2D
    \begin{figure}
      \centering
      \input{visibility.tikz}
      \caption{Examples of visibility in 2D.}
      \label{fig:visibility-2d}
    \end{figure}
